Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2021-10-15 paper/post_tci.tex
Commented on the souble precision of SSIM in Fig. 1 caption

 \begin{figure}[t]
\centering
	\includegraphics[width=0.45\textwidth]{../images/story/post_TCI/story.png}
        \caption{Illustration of the use of priors in reconstruction
          as the number of views reduces. For all cases, the ground
          truth (260$\times$260) appears in the top left.  For
          extremely large number of views (800 views), the standard
          FBP reconstruction (first column) is of very good quality
          (Structural Similarity Index Metric, SSIM=0.92). As the
          number of views become limited (100 views), reconstruction
          using the Total Variation regularization prior (TV, middle
          column) is better both visually and quantitatively than FBP
          (SSIM of 0.96 vs 0.82). If the number of views is
          drastically reduced (20 views), the presence of both TV
          prior and object-prior together with the spatially-varying
          technique of this paper improves the reconstruction
          (SSIM=0.91) when compared to presence of TV-only prior
          (SSIM=0.87) or no prior (SSIM=0.64).}
 \label{fig:story}
 \end{figure}

>>>>

 \begin{figure}[t]
\centering
	\includegraphics[width=0.45\textwidth]{../images/story/post_TCI/story.png}
        \caption{Illustration of the use of priors in reconstruction
          as the number of views reduces. For all cases, the ground
          truth (260$\times$260) appears in the top left.  For
          extremely large number of views (800 views), the standard
          FBP reconstruction (first column) is of very good quality
          (Structural Similarity Index Metric, SSIM=0.92). As the
          number of views become limited (100 views), reconstruction
          using the Total Variation regularization prior (TV, middle
          column) is better both visually and quantitatively than FBP
          (SSIM of 0.96 vs 0.82). If the number of views is
          drastically reduced (20 views), the presence of both TV
          prior and object-prior together with the spatially-varying
          technique of this paper improves the reconstruction
          (SSIM=0.91) when compared to presence of TV-only prior
          (SSIM=0.87) or no prior (SSIM=0.64), an improvement by $4\%$ and $27\%$ respectively (since the ideal SSIM=1).}
 \label{fig:story}
 \end{figure}
